---
title: "Unit 1 Homework"
author: "Put Your Name Here"
date: 'See Canvas for due date'
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

**Directions:** This homework covers material from Unit 1 (Notes 1 - 3). It will be graded as Complete or Incomplete for 3 PER points. To earn a grade of Complete, you will need to:

- make an honest attempt on every question
- submit your .Rmd file and your knitted .html file through Canvas

<br>

If you don’t know how to answer a question, explain your thought process, what you’ve tried, where you looked for help, etc. If questions are left blank or don’t show a good faith effort, you may not receive a grade of Complete. You are encouraged to avoid or minimize AI use as the goal here is to see what you know and to help you prepare for exams and future work. A little friction and struggle is a key part of learning and internalizing new material.

After the homework due date, I will make solutions available, and you will have a chance to complete a Homework Reflection for an additional 3 PER points. If you have questions, let me know!

---

# Load any libraries you use in this homework here

```{r, message = FALSE}
library(dplyr)
```

---

# Part 1 - Warm up

1. Classify each of the following as an argument, function, object, or operator. Put your answer after the colon for each piece of code.

  - `c()`: 
  - `$`: 
  - the `n` in `head(__, n = __)`: 
  - `mario_kart_auction$n_bids`:

<br>



2. Write code to create a vector called `fall_26` that includes the courses you're taking this semester (e.g. "STS 2300").

```{r}
# Put your code below

```

<br>

---

# Part 2 - Mario Kart Example

3. Install the `moderndive` package on your computer if you haven't done so yet. Then, add code in the section above to load the package in this document. Explain below why we do not want to include the code to install the package in this document.

**Answer:** REPLACE THIS WITH YOUR ANSWER

<br>



4. Write code below to bring up the help menu for the `mario_kart_auction` data set from the `moderndive` package. How how many observations are in the data? Give an example of at least one quantitative variable and at least one categorical variable.

```{r}
# Put your code below to bring up the help menu

```

**Number of observations:**

**Quantitative variable(s):**

**Categorical variable(s):**

<br>



5. Use a function to display the number of games that are new vs. used. Then add another line of code that displays the proportion of games that are new vs. used. Make sure the output appears in your document.

```{r}
# Put your code below to explore the data

```

<br>



6. Write code that creates an object called `mario_sample` that includes just the first 15 observations in the data. Add another line of code that prints only the overall auction price (`total_pr`) for those 15 observations. In your answer below, use in-line R code (Hint: we did this in activity 2) to tell someone the highest overall price among your sample of 15 auctions.

```{r}
# Put your code below

```

**Sentence with in-line R code:** 

<br>



7. In the previous question, what type of object is `mario_sample`? What type of object is the 15 overall auction prices?

**mario_sample is:**

**The 15 auction prices are:**

<br>



8. Create a data frame called `mario_summary` that summarizes the data by calculating the following:

  - number of auctions (called `auctions`)
  - mean shipping price (called `avg_ship`)
  - longest auction duration (called `max_length`)
  - standard deviation of the number of bids (called `sd_bids`)

```{r}
# Put your code below

```

<br>



9. Take your code from the previous question and update it below so that a separate summary is calculated for new games and for used games. Call this `mario_comparison`. Your `mario_comparison` data frame will now have two rows (new and used). Is there more variation for number of bids among new games or used games?

```{r}
# Put your code below

```

**Answer:**

<br>



10. Take your `mario_comparison` object and display it below using the `kableExtra` package to format it nicely for this document. Add an option to this code chunk so that your code is **not** displayed in the knitted document. (Note: You should also add code at the top of the document to load `kableExtra` where other packages are loaded.)

```{r}
# Put your code below

```

<br>

---

# Part 3 - Math/Stats Majors Data

11. (4 points) Download the **MTH_STS_Majors.xlsx** file from the Data Files folder on the course Canvas page. Store it in the same location as this .Rmd file. Add code below to read the data set into R as an object called `majors`. (Note: If you need to load any R packages to do this, you should put the code to load them up above.)

```{r}

```

<br>


12. (5 points) Convert the data from wide format to long format. The `Year` and `ArtsSciences` columns will remain the same. Your long format data will have two other columns: `Major` and `Count`. Call this new data frame `majors_long`. (Note: You will likely need to load the `tidyr` package. Add this at the top of the document.)

```{r}
# If you get stuck on an earlier question in this section, let me know so I can
# help out and make sure you can attempt the later questions.


```

<br>


13. Create a new variable in your `majors_long` data frame called `MajorsPer100` that calculates the number of majors per 100 students in the College of Arts and Sciences. This can be done by taking your `Count` variable and dividing by the `ArtsSciences` variable and then multiplying by 100.

```{r}
# If you get stuck on an earlier question in this section, let me know so I can
# help out and make sure you can attempt the later questions.


```

<br>


14. Write code to get rid of the `ArtsSciences` variable from your `majors_long` data frame. Then print the first 4 and last 4 rows of your new data frame so that they show up in your knitted file.

```{r}
# If you get stuck on an earlier question in this section, let me know so I can
# help out and make sure you can attempt the later questions.

```

<br>


15. The code chunk below is set to `eval = FALSE`. Write code using the pipe operator that will accomplish the previous questions in this section all in one step. In other words, you will only use the assignment operator once to go from reading your data in all the way to your finished data frame. (Note: You do not need to print the first and last 4 rows as part of this step.)

```{r, eval = FALSE}

```

<br>


16. In the space below, write a sentence using in-line R code that tells the reader the largest number of Stats majors there have ever been in a year and the average number of Math majors each year. (Note: Make sure you don't get an NA in your knitted document. If this happens, check what argument can remove NAs for your chosen summary functions.)

**Your sentence(s):**

<br>

